---
title: "Whanything-Focus"
output: html_document
---
directories
```{r}
input_file = "/Users/ceshi/Documents/Work/WHAnalysis/transcribed/scripts-2019oct13/coded_2019-10-13_WHanything.csv"
input_dir = "/Users/ceshi/Documents/Work/WHAnalysis/transcribed/scripts-2019oct13"
```



```{r setup, include=FALSE}



library(tidyr)
library(dplyr)
library(ggplot2)
library(viridis)
library(lme4)
# The palette with grey:
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# The palette with black:
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")



setwd(input_dir)
dataset <- read.csv(input_file) 

#names(dataset) <- make.names(names(dataset), unique = TRUE) #this changes all the spaces in names dots 
#dataset contains both test and filler sentences, so need to weed out those first

#each is coded as factor

```

May 21
Adding a new parameter "utt"; specifying whether the utterance is one of the five types:
1. Fragment answer, "a car", code "c"
2. Fragment answer, "apple and a pear", code "a"
3. polar particle "fangle/en/nodding", code "y"
4. polar particle "meifang/en-en/shaking head", code "n"
5. polar particle and elaboration "yes/no, she packed apple and pear", code "e"
6. polar particle and elaboration "yes/no, she didn't pack the car", code "r"
6. other: "o"


Jun 22
- Transcribed more data from adults and kids for Focus, saved under the folder scripts-jun22
- code for whether the answer contains "a car" under "car", and "utt"
- If "a car" is mentioned as an extra information, we code "car" as 0
- Add "yn" collumn 

```{r transform dataset}
#filter out the fillers
df_fc <- filter(dataset, grepl('FC', dataset$expName)) %>% 
  filter(include. != "x",
         grepl("FC", dataset$condition1)
         ) %>% 
  filter(participant != 127,
         participant != 128,
         participant != 132,
         participant != 135,
         participant != 151,
         participant != 153,
         participant != 158,
         participant != 160,
         participant != 161,
         participant != 162,
         participant != 163,
         participant != 163,
         participant != 166,
         participant != 172,
         participant != 179,
         participant != 183,
         participant != 185,
         participant != 201,
         participant != 253,
         participant != 257,
         participant != 259,
         participant != 262,
         participant != 165
         )

#add kids = 1, adults = 0
df_fc$age_group <- as.factor(ifelse(df_fc$participant<500, 1, 0))
#code the two independent variable: wh/np condition
df_fc$whnp <- as.factor(ifelse(grepl('wh', df_fc$expName), 1, 0)) 
#with or without prominance condition
df_fc$foc <-  as.factor(ifelse(grepl('1', df_fc$expName), 1, 0))
#the two measures in this experiment is whether or not kid offer "car"-response
#and the detailed responses given by kids                           
df_fc$car <- ifelse(grepl('c', df_fc$utt), 1, 0)

df_fc$prag <- recode(df_fc$utt, o= "o", y="y", y="y", n="y", a= "a",c="c", e="e", r="e")
df_fc$yn <-   recode(df_fc$prag, o= "o", y = "p", e = "p", a= "a",c="c")
df_fc$polar <- ifelse(df_fc$yn == "p", 1, 0)

```
plotting "car" responses

```{r}
df_fc_sum <- df_fc %>%
 group_by(participant, expName, age_group, whnp,foc) %>% 
  summarize(proportion = mean(car)) %>% 
  group_by(expName, age_group, whnp,foc) %>% 
  summarise(avg_prop = mean(proportion), sd=sd(proportion), n=n()) %>% 
  mutate(SEM = sd/sqrt(n),upper=avg_prop+SEM, lower= avg_prop-SEM)




#df_fc_sum$expName <- factor(df_fc_sum$expName,levels=c("V wh, Wh-question","VnotV wh, Polar quesiton","V NP, Assertion","VnotV NP, Polar question"))

df_fc_sum$expName <- factor(df_fc_sum$expName,levels=c("FC1wh","FC0wh","FC1bn","FC0bn"))

df_fc_sum$foc <- factor(df_fc_sum$foc,levels=c("1","0"))
df_fc_sum$whnp <- factor(df_fc_sum$whnp,levels=c("1","0"))
label_facet <- c("0" ="adults", "1" = "children")
```


Measuring whether the answer is "a car":
```{r}
fc_car <- ggplot(df_fc_sum, aes(x=whnp, y=avg_prop, fill = foc))+
  geom_bar(stat="identity", position = position_dodge(0.9)) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), stat = "identity", width = 0.2, position=position_dodge(0.9)) +
  facet_wrap(~ age_group, labeller=labeller(age_group = label_facet)) +
  labs(y = '% "a car"-responses', x = " ")+ 
  theme(axis.line = element_line(colour = "white"),
    plot.title = element_blank(),
  axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  scale_x_discrete(labels=c("wh","NP")) +
  scale_fill_manual(values=cbPalette[c(2,5)], name = "", breaks=c(1, 0), labels=c("+Prominence", "-Prominence")) +
 # scale_color_manual(name = "", values = cbbPalette[c(1,1)], ) +
  theme_bw()

fc_car
```
Stats on "a car" measure

```{r}
m1_fc <- glmer(formula = car ~foc*whnp+age_group+ (1|participant) +(1|sentence), family = binomial, data = df_fc)
summary(m1_fc)
```

```{r}
m2_fc <- glmer(formula = car ~foc*whnp+ (1|participant) +(1|sentence), family = binomial, data = df_fc)
summary(m2_fc)

```
```{r}
m3_fc <- glmer(formula = car ~foc+whnp+age_group+ (1|participant) +(1|sentence), family = binomial, data = df_fc)
summary(m3_fc)

```
Model comparison
```{r}
AIC(m1_fc, m2_fc, m3_fc)
```

Stats: no random factor, just fix factor

```{r}
glm_fc1 <- glm(car~foc*whnp+age_group, family = binomial, data = df_fc)
summary(glm_fc1)
```

```{r}
glm_fc2 <- glm(car~foc*whnp, family = binomial, data = df_fc)
summary(glm_fc2)
```



```{r}
glm_fc2 <- glm(car~foc+whnp+age_group, family = binomial, data = df_fc)
summary(glm_fc2)
```

```{r}
#stats: no interaction, just focus

#just the kids
dfk_fc <- filter(df_fc, age_group=="1")
m3_fck <- glm(car~foc*whnp, family = binomial, data = dfk_fc)
summary(m3_fck)
#just the adults
dfa_fc <- filter(df_fc, age_group=="0")
m3_fca <- glm(car~foc*whnp, family = binomial, data = dfa_fc)
summary(m3_fca)
```
Measuring whether the answer contains a polar particle:



```{r}
df_fc_polar <- df_fc %>%
 group_by(participant, expName, age_group, whnp,foc, polar) %>% 
  summarize(proportion = mean(polar)) %>% 
  group_by(expName, age_group, whnp,foc) %>% 
  summarise(avg_prop = mean(proportion), sd=sd(proportion), n=n()) %>% 
  mutate(SEM = sd/sqrt(n),upper=avg_prop+SEM, lower= avg_prop-SEM)

df_fc_polar$expName <- factor(df_fc_polar$expName,levels=c("FC1wh","FC0wh","FC1bn","FC0bn"))

df_fc_polar$foc <- factor(df_fc_polar$foc,levels=c("1","0"))
df_fc_polar$whnp <- factor(df_fc_polar$whnp,levels=c("1","0"))
```

Plotting this measurement 
```{r}
fc_polar <- ggplot(df_fc_polar, aes(x=whnp, y=avg_prop, fill = foc))+
  geom_bar(stat="identity", position = position_dodge(0.9)) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), stat = "identity", width = 0.2, position=position_dodge(0.9)) +
  facet_wrap(~ age_group, labeller=labeller(age_group = label_facet)) +
  labs(y = "% yes/no-responses", x = " ")+ 
  theme(axis.line = element_line(colour = "white"),
    plot.title = element_blank(),
  axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  scale_x_discrete(breaks=c(1, 0),labels=c("shenme","NP")) +
  scale_fill_manual(values=c("#0033CC", "#66CCFF"), name = "", breaks=c(1, 0), labels=c("+Prominence", "-Prominence")) +
 # scale_fill_grey(name = "", breaks=c(1, 0), labels=c("+Prominence", "-Prominence")) +
  theme_bw()

fc_polar
```
Stats

```{r}
mfc_pol1 <- glmer(formula = polar ~foc*whnp+age_group+ (1|participant) +(1|sentence), family = binomial, data = df_fc)
summary(mfc_pol1)
print(mfc_pol1,  corr = FALSE)
```
Stats 2: just foc, whnp, no age

```{r}
mfc_pol2 <- glmer(formula = polar ~foc*whnp + (1|participant) +(1|sentence), family = binomial, data = df_fc)
summary(mfc_pol2)

```
```{r}
mfc_pol3 <- glmer(formula = polar ~foc+whnp + (1|participant) +(1|sentence), family = binomial, data = df_fc)
summary(mfc_pol3)

```

```{r}
mfc_pol4 <- glmer(formula = polar ~foc+whnp+age_group + (1|participant) +(1|sentence), family = binomial, data = df_fc)
summary(mfc_pol4)

```
```{r}
mfc_pol5 <- glm(polar~foc+whnp+foc*whnp+age_group, family = binomial, data = df_fc)
summary(mfc_pol5)

```
Model comparison using AIC
```{r}
AIC(mfc_pol1,mfc_pol2,mfc_pol3, mfc_pol4, mfc_pol5)

```

```{r}
df_fc$prag <- recode(df_fc$utt, o= "o", y="y", y ="y", n="y", a= "a",c="c", e="e", r="e", w = "a")
df_fc$yn <-   recode(df_fc$prag, o= "o", y = "p", e = "p", a= "a",c="c")
df_fc$polar <- ifelse(df_fc$yn == "p", 1, 0)

fc_utt <- df_fc %>% 
  group_by(expName, age_group, whnp,foc, prag) %>% 
  summarise(utt_n = n()) 
fc_utt$prag <- factor(fc_utt$prag,levels=c("y","e","o","a","c"))
fc_utt$expName <- factor(fc_utt$expName,levels=c("FC1wh","FC0wh","FC1bn","FC0bn"))
label_facet <- c("0" ="adults", "1" = "children")
```

```{r}
p_fcutt <- ggplot(fc_utt, aes(x=expName, y = utt_n, fill = foc, alpha = prag, color = foc ))+
  geom_bar(stat="identity",position = "fill") +
  facet_wrap(~ age_group, labeller=labeller(age_group = label_facet)) +
    labs(y = "types of answers", x = " ")+ 
  theme(axis.line = element_line(colour = "white"),
    plot.title = element_blank(),
    legend.position = "none",
  #axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  scale_x_discrete(name = "", labels=c("+","-","+","-")) +
  scale_alpha_manual(name = "", values = c(0.1,0.3,0.4,0.5,0.6,1)) +
  scale_fill_manual(name = "", values=cbPalette[c(1,2,1,2,1,2)])+
  scale_color_manual(name = "", values=cbPalette[c(1,2,1,2,1,2)])+
  theme_bw()

  
p_fcutt

```


plotting all utterance types

```{r}
p_fcutt_noshow <- ggplot(fc_utt, aes(x=expName, y = utt_n, fill = prag))+
  geom_bar(stat="identity",position = "fill") +
  facet_wrap(~ age_group, labeller=labeller(age_group = label_facet)) +
    labs(y = "% of responses", x = " ")+ 
  theme(axis.line = element_line(colour = "white"),
    plot.title = element_blank(),
    legend.position = "none",
  #axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 45, hjust = 2)
  ) +
  scale_x_discrete(name = "", labels=c("+","-","+","-")) +
  #scale_alpha_manual(name = "", values = c(0.3,0.4,0.5,0.6,1)) +
  scale_fill_manual(name = "", breaks = c("y","e","o","a","c"), values=cbPalette[c(6,3,1,4,5)], labels = c('"No"','"No, a pear and an apple"', '"Other"', '"A pear and an apple"', '"A car"'))+
  #scale_color_manual(name = "", values=cbPalette[c(2,1,2,1)])+
  theme_bw()

  
p_fcutt_noshow
```




YN experiment
First plot using "fragment answer" as the measurement
```{r}
df_yn <- filter(dataset, grepl('YN', type))
  
df_yn$age_group <- as.factor(ifelse(df_yn$participant<500, 1, 0))
df_yn$whnp <- as.factor(ifelse(grepl('wh', df_yn$expName), 1, 0))
df_yn$vnotv <-  as.factor(ifelse(grepl('1', df_yn$expName), 1, 0))
#df_yn$wh_resp <-  as.factor(ifelse(grepl('w', df_yn$prag), 1, 0))
#df_yn <- separate(df_yn, audio, c("sentence", "no"), sep = -1)
df_yn$utt <- recode(df_yn$utt, o= "o", y="y", y ="y", n="y", a= "a",c="c", e="e", r="e")
df_yn$yn <-   recode(df_yn$utt, o= "o", y = "p", e = "p", a= "a",c="c")
df_yn$polar <- ifelse(df_yn$yn == "p", 1, 0)


df_yn_polar <- df_yn %>%
 group_by(participant, expName, age_group, whnp,vnotv) %>% 
  summarize(proportion = mean(polar)) %>% 
  group_by(expName, age_group, whnp,vnotv) %>% 
  summarise(avg_prop = mean(proportion), sd=sd(proportion), n=n()) %>% 
  mutate(SEM = sd/sqrt(n),upper=avg_prop+SEM, lower= avg_prop-SEM)

df_yn_polar$expName <- factor(df_yn_polar$expName,levels=c("YN1wh","YN0wh","YN1bn","YN0bn"))

df_yn_polar$vnotv <- factor(df_yn_polar$vnotv,levels=c("1","0"))
df_yn_polar$whnp <- factor(df_yn_polar$whnp,levels=c("1","0"))
```



```{r}

#df_yn_sum$expName <- factor(df_yn_sum$expName,levels=c("V wh, Wh-question","VnotV wh, Polar quesiton","V NP, Assertion","VnotV NP, Polar question"))

label_facet <- c("0" ="adults", "1" = "children")

df_yn_polar$vnotv <- factor(df_yn_polar$vnotv,levels=c("0","1"))
df_yn_polar$whnp <- factor(df_yn_polar$whnp,levels=c("1","0"))

yn_plot <- ggplot(df_yn_polar, aes(x=whnp, y=avg_prop, fill=vnotv))+
  geom_bar(stat="identity", position = position_dodge(0.9)) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), stat = "identity", width = 0.2, position=position_dodge(0.9)) +
  facet_wrap(~ age_group, labeller=labeller(age_group = label_facet)) +
    labs(y = "% yes/no responses", x = " ")+ 
  theme(axis.line = element_line(colour = "white"),
    plot.title = element_blank(),
  axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  scale_x_discrete(labels=c(c("wh","NP"))) +
  scale_fill_manual(values=c("#0033CC", "#66CCFF"), name = "", breaks=c(0, 1), labels=c("V", "V-not-V"))
  #scale_fill_grey(name = "", breaks=c(0, 1), labels=c("V", "VnotV"))+
  theme_bw()
  
  
  
  yn_plot
  
```

"#99FF99","#006600" green
```{r}
df_yn$ap <- ifelse(df_yn$utt == "a", 1, 0)


df_yn_ap <- df_yn %>%
 group_by(participant, expName, age_group, whnp,vnotv) %>% 
  summarize(proportion = mean(ap)) %>% 
  group_by(expName, age_group, whnp,vnotv) %>% 
  summarise(avg_prop = mean(proportion), sd=sd(proportion), n=n()) %>% 
  mutate(SEM = sd/sqrt(n),upper=avg_prop+SEM, lower= avg_prop-SEM)

df_yn_ap$expName <- factor(df_yn_ap$expName,levels=c("YN1wh","YN0wh","YN1bn","YN0bn"))

df_yn_ap$vnotv <- factor(df_yn_ap$vnotv,levels=c("0","1"))
df_yn_ap$whnp <- factor(df_yn_ap$whnp,levels=c("1","0"))

p_ynap <- ggplot(df_yn_ap, aes(x=whnp, y=avg_prop, fill=vnotv))+
  geom_bar(stat="identity", position = position_dodge(0.9)) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), stat = "identity", width = 0.2, position=position_dodge(0.9)) +
  facet_wrap(~ age_group, labeller=labeller(age_group = label_facet)) +
    labs(y = "% 'an apple and a pear' responses", x = " ")+ 
  theme(axis.line = element_line(colour = "white"),
    plot.title = element_blank(),
  axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  scale_x_discrete(labels=c(c("wh","NP"))) +
  scale_fill_manual(values=c("#006600","#99FF99"), name = "", breaks=c(0, 1), labels=c("V", "V-not-V"))
  #scale_fill_grey(name = "", breaks=c(0, 1), labels=c("V", "VnotV"))+
  theme_bw()
  
  
  
p_ynap
```



Stats
Interaction
```{r}
myn_pol1 <- glmer(formula = polar ~vnotv*whnp+age_group + (1|participant) +(1|sentence), family = binomial, data = df_yn)
summary(myn_pol1)
```
No agegroup

```{r}
myn_pol2 <- glmer(formula = polar ~vnotv*whnp + (1|participant) +(1|sentence), family = binomial, data = df_yn)
summary(myn_pol2)
```

No interaction
```{r}
myn_pol3 <- glmer(formula = polar ~vnotv+whnp+age_group + (1|participant) +(1|sentence), family = binomial, data = df_yn)
summary(myn_pol3)
```
```{r}
myn_pol4 <- glmer(formula = polar ~vnotv+whnp + (1|participant) +(1|sentence), family = binomial, data = df_yn)
summary(myn_pol4)
```

```{r}
AIC(myn_pol1,myn_pol2,myn_pol3,myn_pol4)
```


Only kids

```{r}
yn_k <-filter(df_yn, age_group =="1")
myn_k1 <- glmer(formula = polar ~vnotv*whnp + (1|participant) +(1|sentence), family = binomial, data = yn_k)
summary(myn_k1)

glmyn_k1 <- glm(formula = polar~vnotv*whnp, data = yn_k)
summary(glmyn_k1)
```
```{r}
yn_a <-filter(df_yn, age_group =="0")
myn_a1 <- glmer(formula = polar ~vnotv*whnp + (1|participant) +(1|sentence), family = binomial, data = yn_a)
summary(myn_a1)


glmyn_a2 <- glm (formula = polar ~ vnotv*whnp, data = yn_a)
summary(glmyn_a2)
```


Elaborate on the types of answers that participants give, using a stacked plot
```{r}
df_yn$prag <- recode(df_yn$utt, o= "o", y="y", y ="y", n="y", a= "a",c="c", e="e", r="e", w = "a")
df_yn$yn <-   recode(df_yn$prag, o= "o", y = "p", e = "p", a= "a",c="c")
df_yn$polar <- ifelse(df_yn$yn == "p", 1, 0)

```


```{r}
yn_utt <- df_yn %>% 
  group_by(expName, age_group, whnp,vnotv, prag) %>% 
  summarise(utt_n = n()) 
yn_utt$prag <- factor(yn_utt$prag,levels=c("y","e","o","c","a"))
yn_utt$expName <- factor(yn_utt$expName,levels=c("YN0wh","YN1wh","YN0bn","YN1bn"))
label_facet <- c("0" ="adults", "1" = "children")
p_ynutt <- ggplot(yn_utt, aes(x=expName, y = utt_n, fill = vnotv, alpha = prag, color = vnotv ))+
  geom_bar(stat="identity",position = "fill") +
  facet_wrap(~ age_group, labeller=labeller(age_group = label_facet)) +
    labs(y = "types of answers", x = " ")+ 
  theme(axis.line = element_line(colour = "white"),
    plot.title = element_blank(),
    legend.position = "none",
  #axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  scale_x_discrete(name = "", labels=c("V","VnotV","V","VnotV")) +
  scale_alpha_manual(name = "", values = c(0.3,0.4,0.5,0.6,1)) +
  scale_fill_manual(name = "", values=cbPalette[c(2,1,2,1)])+
  scale_color_manual(name = "", values=cbPalette[c(2,1,2,1)])+
  theme_bw()

  
p_ynutt
```

```{r}
label_facet <- c("0" ="adults", "1" = "children")
p_ynutt_notshown <- ggplot(yn_utt, aes(x=expName, y = utt_n, fill = prag))+
  geom_bar(stat="identity",position = "fill") +
  facet_wrap(~ age_group, labeller=labeller(age_group = label_facet)) +
    labs(y = "types of answers", x = " ")+ 
  theme(axis.line = element_line(colour = "white"),
    plot.title = element_blank(),
    legend.position = "none",
  #axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  scale_x_discrete(name = "", labels=c("V","VnotV","V","VnotV")) +
  scale_fill_manual(name = "", breaks = c("y","e","o","c","a"), values=cbPalette[c(6,3,1,5,4)], labels = c('"Yes"','"Yes, an apple and a pear"', '"Other"', '"A car"', '"An apple and a pear"'))+
  theme_bw()
p_ynutt_notshown
```


FC0wh = "Wh-Focus, Assertion", FC1wh = "Wh+Focus, Wh-question", FC0bn = "NP-Focus, Assertion", FC1bn = "NP+Focus, Assertion", 


a_dens <- ggplot(a_hist, aes(x=test, y= n, fill= e)) +
  geom_bar(stat="identity", width = 0.5, position = position_dodge(0.9)) + 
  facet_grid(e~m, labeller=labeller(m = labelm, e= labele)) + 
  labs(title=paste0("Mandarin adults, n=", 
                    length(unique(df_wide_adults$participant))), 
       x = "%of yes-response", y  = "No.of participants") +
  scale_fill_manual(values=cbPalette[c(4,1)], name="Complement Truth", breaks=c("T", "F")) 
print(a_dens)

```{r}
yn_hist=df_yn %>%group_by(participant, expName, age_group, whnp,vnotv) %>%summarize(proportion = mean(as.numeric(wh_resp))-1)  %>%
  group_by(age_group,whnp,vnotv, proportion) %>% summarise(n=n())%>%
  filter(age_group=="1") #kids only

yn_hist$vnotv <- factor(yn_hist$vnotv,levels=c("1","0"))
yn_hist$whnp <- factor(yn_hist$whnp,levels=c("1","0"))

lwhnp <- c("1"="wh", "0"="NP")
lvnotv <- c("1"="VnotV","0"="V")

yn_dens <-  ggplot(yn_hist, aes(x=proportion, y= n, fill= vnotv)) +
  geom_bar(stat="identity") + 
  facet_grid(whnp ~ vnotv, labeller=labeller(whnp = lwhnp, vnotv= lvnotv)) + 
  labs(x = "%of wh-response", y  = "No.of participants") +
  scale_fill_manual(values=cbPalette[c(1,2)], name="", labels = lvnotv) +
  theme_bw()
print(yn_dens)
```


```{r}
fc_hist=df_fc %>%group_by(participant, expName, age_group, whnp,foc) %>%summarize(proportion = mean(as.numeric(wh_resp))-1)  %>%
  group_by(age_group,whnp,foc, proportion) %>% summarise(n=n())%>%
  filter(age_group=="1") #kids only

fc_hist$vnotv <- factor(fc_hist$foc,levels=c("1","0"))
fc_hist$whnp <- factor(fc_hist$whnp,levels=c("1","0"))

lwhnp <- c("1"="wh", "0"="NP")
lfoc <- c("1"="+Focus","0"="-Focus")


  
  
  
fc_dens <-  ggplot(fc_hist, aes(x=proportion, y= n, fill= foc)) +
  geom_bar(stat="identity") + 
  facet_grid(whnp ~ foc, labeller=labeller(whnp = lwhnp, foc= lfoc)) + 
  labs(x = "%of wh-response", y  = "No.of participants") +
  scale_fill_manual(values=cbPalette[c(1,4)], name="", labels = lfoc) +
  theme_bw()
fc_dens
```
```{r}
#zoom in on the FCwh conditions, esp when they give wh answers
fc_ans = df_fc %>% filter(wh_resp== 1) %>% filter(age_group==1)
fc_ans <- fc_ans %>% 
 group_by(participant, expName, age_group, whnp,foc) %>% 
  summarize(proportion = mean(as.numeric(ans))-1) %>% 
  group_by(age_group,whnp,foc) %>% summarise(avg_prop = mean(proportion), sd=sd(proportion), n=n()) %>% 
  mutate(SEM = sd/sqrt(n),upper=avg_prop+SEM, lower= avg_prop-SEM)%>%
  filter(age_group=="1") #kids only

fc_ans

fc_wh_plot <- ggplot(fc_ans, aes(x=whnp, y=avg_prop, fill = foc))+
  geom_bar(stat="identity", position = position_dodge(0.9)) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), stat = "identity", width = 0.2, position=position_dodge(0.9)) +
  #facet_wrap(~ age_group, labeller=labeller(age_group = label_facet)) +
  labs(y = "% car-responses", x = "")+ 
  #theme(axis.line = element_line(colour = "white"),
 #   plot.title = element_blank(),
 # axis.title.x = element_blank(),
 # axis.text.x = element_text(angle = 45, hjust = 1)
 # ) +
  scale_x_discrete(labels=c("wh","NP")) +
  scale_y_continuous(limits=c(0, 1)) +
  scale_fill_manual(values=cbPalette[c(1,2)], name = "", breaks=c(0, 1), labels=c("-Prominence", "+Prominence")) 
fc_wh_plot




fc_ans_dens <-  ggplot(fc_ans, aes(x=proportion, y= n, fill= foc)) +
  geom_bar(stat="identity") + 
  facet_grid(whnp ~ foc, labeller=labeller(whnp = lwhnp, foc= lfoc)) + 
  labs(x = "%of wh-response", y  = "No.of participants") +
  scale_fill_manual(values=cbPalette[c(1,4)], name="", labels = lfoc) +
  theme_bw()+
  scale_x_continuous(breaks=c(0.0,0.25,0.5,0.75,1.0)) +
  scale_y_continuous(limits=c(0, 3), breaks=c(0,1,2,3))

fc_ans_dens
```

The statistics
```{r}
df_fc_k = filter(df_fc, age_group==1)
df_yn_k = filter(df_yn, age_group==1)
m1 <- glmer(formula = wh_resp ~age_group*whnp*vnotv+(1|participant)+(1|no), family = binomial, data = df_yn)
m2 <- glmer(formula = wh_resp ~age_group+(1|participant)+(1|no), family = binomial, data = df_yn)
m3 <- glmer(formula = wh_resp ~whnp+(1|participant)+(1|no), family = binomial, data = df_yn)
m4 <- glm(wh_resp~age_group+whnp, family = binomial, data = df_yn) 

m5 <- glmer(formula = wh_resp ~whnp+vnotv+(1|participant)+(1|no), family = binomial, data = df_yn_k)
m6 <- glm(wh_resp~vnotv+whnp, family = binomial, data = df_yn_k) 


summary(m1)
summary(m2)
summary(m3)
summary(m4)
summary(m5)
summary(m6)
broom::tidy(m3)
exp(broom::tidy(m3)$estimate)

df_fc$car <- as.factor(df_fc$car)
#m1_fc <- glmer(formula = car ~ age_group*whnp*foc+ (1|participant)+(1|no), family = binomial, data = df_fc)
m2_fc <- glmer(formula = car ~foc*whnp+ (1|participant) +(1|no), family = binomial, data = df_fc)

m3_fc <- glm(car~foc+whnp+age_group, family = binomial, data = df_fc)

m4_fc <- glm(car~foc+whnp+foc*whnp, family = binomial, data = df_fc)

m5_fc <- glm(car~foc, family = binomial, data = df_fc)

m6_fc <- glm(car~foc*whnp, family = binomial, data = df_fc)

m7_fc <- glmer(formula = car ~foc + whnp + (1|participant) +(1|no), family = binomial, data = df_fc)

m8_fc <- glm(car~whnp+foc, family = binomial, data = df_fc)
m9_fc <- glmer(formula = car ~foc+whnp+ (1|participant) +(1|no), family = binomial, data = df_fc_k)
summary(m2_fc)
summary(m3_fc)
summary(m4_fc)
summary(m6_fc)
summary(m8_fc)
summary(m9_fc)

broom::tidy(m2_fc)
exp(broom::tidy(m2_fc)$estimate)

broom::tidy(m3_fc)
exp(broom::tidy(m3_fc)$estimate)


broom::tidy(m7_fc)
exp(broom::tidy(m7_fc)$estimate)
```

